---
title: "STAT 545B Assignment B1"
output: github_document
---

Welcome to my STAT 545B assignment b1! 
Below, I will practice making a function in R, documenting it, and testing it.


### Loading packages

Before I start, I will load the packages needed in my subsequent workflow.

```{r, message = FALSE}
# Load packages
library(testthat)
```


### Writing a function

I want to create a function that is not dependent on external packages, so I stick with base r.
I like math equations and I decide to calculate the consecutive difference for a series of numbers. 
Below, the `title`, `@description`, `@param`, and  `@return` are documented alongside my function.

```{r}

# Calculate the consecutive difference for a sequence of numbers

# @description
# given a sequence such as (x1, x2, x3, x4, x5, ...), 
# consecutive_diff() can calculate all the consecutive differences as {(x2-x1), (x3-x2), (x4-x3), ...}


# @param number_sequence 
#   the number sequence the user chooses to put in this function. 
#   I use `number_sequence` because I think it's the most intuitive name.


# @return consecutive_diff() returns a numeric vector

consecutive_diff <- function(number_sequence){
  # special case, check if the input vector is empty 
  if(length(number_sequence) == 0){
    stop("Sorry, the input number sequence is empty, please input a non-empty number sequence!")
  }
  
  # special case, check if the input vector only contains one number
  if(length(number_sequence) == 1){
    stop("Sorry, your output vector has a length of 0, 
         please input a number sequence with at least two numbers for the function to work properly:)")
  }
  
  # if the sequence contains NAs, provide a message.
  if (any(is.na(number_sequence))) {
    message("The input number sequence contains NAs.")
  }
  x2 <- number_sequence[-1]
  x1 <- number_sequence[-length(number_sequence)]
  return(x2 - x1)
}


```



### Examples

Here, I include two examples using the function I created above.

```{r}

# example 1
# create an array of consecutive squares and calculate the consecutive differences  

lst <- c(0, 1, 4, 9, 16, 25, 36, 49, 64)
consecutive_diff(lst)


```


```{r}

# example 2 
# generate a series of random integers and calculate the consecutive difference
consecutive_diff(sample.int(100,20))

```



### Testing the function

It's time to test my function. Here, I  use three non-redundant uses of an `expect_()` function from the `testthat` package.

```{r}
test_that("Test the consecutive number difference function", {
  expect_error(consecutive_diff(c()), "Sorry, the input number sequence is empty, please input a non-empty number sequence!")
  expect_message(consecutive_diff(c(1,6,11,9, 2, NA)), "The input number sequence contains NAs.")
  expect_equal(consecutive_diff(c(replicate(5,1))), c(0,0,0,0))
})
```

