---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ConsecutiveDifference

<!-- badges: start -->
<!-- badges: end -->

The goal of `ConsecutiveDifference` is to provide an easy way for calculating the consecutive difference for a sequence of numbers. It contains one function called `consecutive_diff()`. 

## Installation

You can install the development version of ConsecutiveDifference from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("https://github.com/stat545ubc-2022/ming-assignment-b1")

```


## Usage

For instance, given a sequence such as (x1, x2, x3, x4, x5, ...), `consecutive_diff()` can calculate all the consecutive differences as {(x2-x1), (x3-x2), (x4-x3), ...}.

```{r, eval=FALSE}
library(ConsecutiveDifference)

# get the consecutive differences of an input number list
lst <- c(10,9,6,2,15,7)
consecutive_diff(lst)

```




